\documentclass[]{article}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{everypage}

\newcommand{\Lpagenumber}{\ifdim\textwidth=\linewidth\else\bgroup
  \dimendef\margin=0 %use \margin instead of \dimen0
  \ifodd\value{page}\margin=\oddsidemargin
  \else\margin=\evensidemargin
  \fi
  \raisebox{\dimexpr -\topmargin-\headheight-\headsep-0.5\linewidth}[0pt][0pt]{%
    \rlap{\hspace{\dimexpr \margin+\textheight+\footskip}%
    \llap{\rotatebox{90}{ CV  - Erik Marsja 
- \thepage\hspace{1pt}(\pageref{LastPage})}}}}%
\egroup\fi}
\AddEverypageHook{\Lpagenumber}%

\usepackage{adjustbox}
\usepackage{titling}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{titlesec}
\usepackage[scaled=.80]{helvet}% Helvetica, served as a model for arial

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.0pt}
\fancyfoot[CO,CE]{   Erik Marsja -  \thepage\hspace{1pt}(\pageref{LastPage})}
\fancypagestyle{plain}{\pagestyle{fancy}}

\usepackage[margin=1in]{geometry}

% Font awesome
\usepackage{fontawesome}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% For tables


% Tightlist

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% URLS
\usepackage[hidelinks]{hyperref}
\usepackage{breakurl}
\usepackage{float} % here for H placement parameter

% Appendix header style

\fancypagestyle{style2}{
\fancyhf{}
\fancyhead[C]{Appendix 1}
}


% For Changing the margins (Education)

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

%For displaying the table in landscape format
\usepackage[absolute]{textpos}

\fancypagestyle{lscape}{% 
\fancyhf{} % clear all header and footer fields 
\fancyfoot[LE]{%
\begin{textblock}{20}(1,5){\rotatebox{90}{\leftmark}}\end{textblock}
\begin{textblock}{1}(13,10.5){\rotatebox{90}{\thepage}}\end{textblock}}
\fancyfoot[LO] {%
\begin{textblock}{1}(13,10.5){\rotatebox{90}{\thepage}}\end{textblock}
\begin{textblock}{20}(1,13.25){\rotatebox{90}{\rightmark}}\end{textblock}}
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt}}

\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}

% Appendix
\fancypagestyle{style2}{
\fancyhf{}
\fancyhead[C]{Appendix 1}
\renewcommand{\headrulewidth}{1pt}
}



\newcommand\secbar {
    \tikz[baseline, trim left=3.2cm] 
    {
        \fill [white] (3cm,0.1ex) rectangle +(0.2cm,1.1ex);
        \draw [gray!95, fill=gray!80] (0cm,0.1ex) rectangle (3cm,1.1ex);        
    }
}
\newcommand\subsecbar {
    \tikz[baseline, trim left=0.15cm] 
    {
        \fill [white] (2cm,0.1ex) rectangle +(0.2cm,1.1ex);
        \fill [blue!40] (0cm,0.1ex) rectangle (2cm,1.1ex);      
    }
}

\newcommand\subsubsecbar {
    \tikz[baseline, trim left=0.15cm] 
    {
        \fill [white] (1cm,0.1ex) rectangle +(0.2cm,1.1ex);
        \fill [blue!40] (0cm,0.1ex) rectangle (2cm,1.1ex);      
    }
}

\titleformat{\section}{\large}{}{0cm}{\secbar}
\titleformat{\subsection}{\large}{}{0cm}{\normalfont\sffamily\Large\bfseries\subsecbar}
\titleformat{\subsubsection}{}{}{0cm}{\normalfont\sffamily\large\bfseries}

% No first line paragraph indent
\usepackage{parskip}
\usepackage{enumitem}

\setlength{\parskip}{0cm}


\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{1pt plus 1pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{1pt plus 1pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

\begin{document}

\centerline{\huge \textbf{Erik
Marsja} | \textcolor{darkgray}{Publikationslista}}

\vspace{1mm}

\hrule

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}lYl@{}}
\textbf{Home Address}: & & 
\\Tvistevägen 26, SE-907 36 Umeå, Sweden & & 
\\\\

 \faPhone \hspace{1 mm}  +4670-36 33
662  \hspace{1 mm}  &  & \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:erik.marsja@liu.se}{\nolinkurl{erik.marsja@liu.se}}} \hspace{1 mm}  \\
 \faGlobe \hspace{1 mm} \href{http://www.marsja.se}{\tt www.marsja.se}   &  & \faGithub \hspace{1 mm} \href{http://github.com/marsja}{\tt marsja} \hspace{1 mm}  \\
 \multicolumn{3}{c}{}
 \\\hline
\end{tabularx}
\end{table}

\hypertarget{publikationer}{%
\subsection{Publikationer}\label{publikationer}}

\hypertarget{refereebeduxf6mda-original-artiklar}{%
\subsubsection{Refereebedömda
original-artiklar}\label{refereebeduxf6mda-original-artiklar}}

Totalt: 7

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Stenbäck, V., \textbf{Marsja}, E., Ellis, R., \& Rönnberg, J.
  (Accepted). Relationships between objective and subjective outcome
  measures of speech recognition in noise. \emph{International Journal
  of Audiology}. (\emph{Open Access})
\item
  \textbf{Marsja}, E., Stenbäck, V., Moradi, S., Danielsson, H., \&
  Rönnberg, J. (2022). Is Having Hearing Loss Fundamentally different?
  Multi-group structural equation modeling of the effect of cognitive
  functioning on speech identification. \emph{Ear and Hearing}.
  \url{https://doi.org/10.1097/AUD.0000000000001196} (\emph{Open
  Access}). R-skript tillgänglig:
  \url{https://github.com/marsja/EANDH-D-21-00145}
\item
  Stenbäck, V., \textbf{Marsja}, E., Hällgren, M., Lyxell, B., \&
  Larsby, B. (2021). The Contribution of Age, Working Memory Capacity,
  and Inhibitory Control on Speech Recognition in Noise in Young and
  Older Adult Listeners. \emph{Journal of Speech, Language, and Hearing
  Research, 64}(11), 4513--4523.
  \url{https://doi.org/10.1044/2021_JSLHR-20-00251}
\item
  Rosa, E., \textbf{Marsja}, E., \& Ljungberg, J. K. (2020). Exploring
  Residual Capacity: The Effectiveness of a Vibrotactile Warning During
  Increasing Levels of Mental Workload in Simulated Flight Tasks.
  \emph{Aviation Psychology and Applied Human Factors, 10(1)}, 13--23.
  \url{https://doi.org//10.1027/2192-0923/a000180}
\item
  \textbf{Marsja}, E., Marsh, J.E., Hansson, P., \& Neely, G. (2019).
  Examining the Role of Spatial Changes in Bimodal and Uni-Modal
  To-Be-Ignored Stimuli and How They Affect Short-Term Memory Processes.
  \emph{Frontiers In Psychology}.
  \url{https://doi.org/10.3389/fpsyg.2019.00299} - \textbf{Del av
  avhandling} (\emph{Open Access}).
\item
  \textbf{Marsja}, E., Neely, G., \& Ljungberg, K.J. (2018).
  Investigating Deviance Distraction and the Impact of the Modality of
  the To-Be-Ignored Stimuli. \emph{Experimental Psychology, 65(2)},
  61--70. \url{http://doi.org/10.1027/1618-3169/a000390} - \textbf{Del
  av avhandling}. R-skript och data tillgänglig:
  \url{https://osf.io/amd2h/}.
\item
  Ljungberg, K. J., Parmentier, F. B. R., Jones, D. M., \textbf{Marsja},
  E., \& Neely, G. (2014). ``What's in a name?'' ``No more than when
  it's mine own''. Evidence from auditory oddball distraction.
  \emph{Acta Psychologica, 150C}, 161--166.
  \url{http://dx.doi.org/10.1016/j.actpsy.2014.05.009}
\end{enumerate}

\hypertarget{konferensbidrag}{%
\subsection{Konferensbidrag}\label{konferensbidrag}}

Totalt: 12

Se ``Deltagande i nationella och internationella konferenser'' för mer
information.

\hypertarget{refereegranskade}{%
\subsubsection{Refereegranskade}\label{refereegranskade}}

Totalt: 2

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Marsja}, E., Neely G., Ma, L., \& Ljungberg K.J., (2015,
  August). Cross-modality matches of intensity and attention capture
  dimensions of auditory and vibrotactile stimuli. Proceedings for the
  31st Annual Meeting of the International Society for Psychophysics,
  Québec, CA. Retrieved from
  \url{https://proceedings.fechnerday.com/index.php/proceedings/article/view/584}
\item
  \textbf{Marsja}, E., Neely, G., Parmentier, F.B.R., \& Ljungberg, K.J.
  (2013, October). Maintenance of the distractive effect of deviating
  vibrotactile stimuli in a cross-modal oddball paradigm. Proceedings of
  the 29th Annual meeting of the International Society of Psychophysics,
  Freiburg, DE. Retrieved from
  \url{https://proceedings.fechnerday.com/index.php/proceedings/article/view/579}
\end{enumerate}

\hypertarget{ej-refereegranskade}{%
\subsubsection{Ej refereegranskade}\label{ej-refereegranskade}}

Totalt: 10

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Marsja}, E., Danielsson, H., Stenbäck, V., Moradi, S.,
  Rönnberg, J. (2019, November). Examining how Cognitive Functioning,
  Aging, and Hearing Loss, Affect Speech-in-Noise Performance. Aging and
  Speech Communication Conference, Tampa, Florida, USA.
\item
  Stenbäck, V., \textbf{Marsja}, E., Danielsson, H., Rönnberg, J. (2019,
  November). Logical and Auditory Inference Making: Performance in the
  HINT in normally-hearing and hearing-impaired listeners. Aging and
  Speech Communication Conference, Tampa, Florida, USA.
\item
  Bampouni, E., \textbf{Marsja}, E., Sörman, D.E., \& Ljungberg, K.J
  (2019, November). Do Action Gamers Have Enhanced Visual Search Skills?
  a Realistic Task Approach. The 15th SweCog conference of the Swedish
  Cognitive Science Society, Umeå, Sweden.
\item
  \textbf{Marsja}, E., Danielsson, H., Stenbäck, V., Moradi, S., \&
  Rönnberg, J. (2019, June). Examining Relationship Amongst Cognition,
  Hearing Loss, Age, \& Speech in Noise. Cognitive Hearing Science for
  Communication, Linköping, Sweden. Poster.
\item
  Stenbäck, V., Moradi, S., \textbf{Marsja}, E., Danielsson, H., \&
  Rönnberg, J. (2019, June). Logical and auditory inference-making in
  normally-hearing and hearing-impaired listeners. Cognitive Hearing
  Science for Communication, Linköping, Sweden.
\item
  \textbf{Marsja}, E., Marsh, J.E., Neely G., Hansson P., \& Ljungberg
  K.J. (2017, April). Domain-generality or domain-specificity of the
  short-term memory: insights from a multisensory distraction paradigm.
  Re-thinking the Senses Spring School, Dubrovnik, Croatia.
\item
  \textbf{Marsja}, E., Marsh, J.E., Neely G., Hansson P., \& Ljungberg
  K.J. (2016, September). Do Spatial Changes in Sounds and Vibrations
  Affect Visuo-spatial and Verbal Short-Term Memory? Attention and
  Control: Insights from Distraction, Workshop, University of Central
  Lancashire, Preston, UK. Invited presentation.
\item
  \textbf{Marsja}, E., Marsh, J.E., Neely G., Hansson P., \& Ljungberg
  K.J. (2016, June). Spatial Change in Multisensory Distractors Impact
  on Verbal and Spatial Short Term Memory. International Multisensory
  Research Forum 17th annual meeting, Suzhou, CHN. Oral presentation.
\item
  \textbf{Marsja}, E., Neely, G., Parmentier, F.B.R., \& Ljungberg, K.J.
  (2014, October) Deviance Distraction Is Contingent on Stimuli Being
  Presented within the Same Modality. Psychonomic Society's 55th Annual
  Meeting. Long Beach, CA, USA.
\item
  Ljungberg, K.J., Parmentier, F.B.R., \textbf{Marsja}, E., Neely, \& G.
  Jones, D., (2014, January). Any Tom, Dick, or Harry will do: Hearing
  one's own name distracts no more than any other in a cross-modal
  oddball task. Experimental Psychology Society Meeting. London, UK.
\end{enumerate}

\hypertarget{populuxe4rvetenskapliga-artiklar}{%
\subsection{Populärvetenskapliga
Artiklar}\label{populuxe4rvetenskapliga-artiklar}}

Totalt: 1

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Marsja}, E. (2016, July). Python Programming in Psychology --
  From Data Collection to Analysis. \emph{JEPS Bulletin - The Official
  Blog of the Journal of European Psychology Students}. \textbf{Invited
  Blog Post}. Retrieved from \sloppy
  \url{http://blog.efpsa.org/2016/07/12/python-programming-in-psychology-from-data-collection-to-analysis/}
\end{enumerate}

\end{document}